---
title: "Introduction to R"
author: "Rushikesh"
date: "14/09/2020"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Welcome - R Markdown

```{r Install Packages, include=FALSE}
install.packages("dplyr",repos = "http://cran.us.r-project.org")
install.packages("sqldf",repos = "http://cran.us.r-project.org")
install.packages("car",repos = "http://cran.us.r-project.org")
install.packages("tidyquant",repos = "http://cran.us.r-project.org")
install.packages("flexdashboard",repos = "http://cran.us.r-project.org")
install.packages("plotly",repos = "http://cran.us.r-project.org")

```

***
Welcome, R is a programming language and free software environment for statistical computing and graphics supported by the R Foundation for Statistical Computing. The R language is widely used among statisticians and data miners for developing statistical software and data analysis.

```{r Load Packages, include=FALSE}
library(dplyr)
library(sqldf)
library(plotly)

```

```{r import csv data, include=FALSE}

my_data <- read.csv("Lin_Reg_R.csv")

View(my_data)

quantile(my_data$Losses,c(0,0.01,0.05,0.25,0.5,0.75,1))

summary(my_data)
```

### Data Wrangling

```{r Data Wrangling, include=FALSE}

## base , dplyr , sqldf
# Select Data 
my_data %>% select(Age, Gender)

# Filter Data
my_data %>% select(Age, Gender) %>% filter(Gender == "M")

# Mutate Data 
my_data <- my_data %>% mutate(new_losses = my_data$Losses * 1.5)

my_data <- my_data %>% mutate(capped_losses = NULL)

# Remove Null
my_data %>% filter(!is.na(my_data$Married))

# Summarize Data
my_data %>% group_by(Gender) %>% summarize(n())

table(my_data$Married)

# Condition if else (Managing Outlier)

my_data$capped_losses <- ifelse(my_data$Losses < 32,32 ,ifelse(my_data$Losses > 1500, 1500, my_data$Losses))

my_data$Gender_Dummy <- ifelse(my_data$Gender == "M", 1 , 0)

my_data$Marriage_Dummy <- ifelse(my_data$Married == "Married", 1 , 0)

my_data$Fuel_Dummy <- ifelse(my_data$Fuel.Type == "P", 1 , 0)

View(my_data)

## Bonus Library for SQL users
library(sqldf)

sqldf("select * from my_data")

my_sql_query_data <- sqldf("select Gender , count(Gender) from my_data group by Gender")

sqldf("select max(Losses) from my_data")

sqldf("select min(Losses) from my_data")

```

***
Data wrangling, sometimes referred to as data munging, is the process of transforming and mapping data from one "raw" data form into another format with the intent of making it more appropriate and valuable for a variety of downstream purposes such as analytics.

### Plotting Graphs - Histogram

```{r Lets Plot}

# base , ggplot , plot_ly

# ?hist Not sure about something use R help 

hist(my_data$Age)

```

### Plotting Graphs - Histogram 2
```{r}

# histogram with added parameters
hist(my_data$Age,
main= paste("Histogram of" , "Age"),
xlab="Temperature in degrees Fahrenheit",
xlim=c(10,80),
#ylim = c(0,2500),
col="darkmagenta",
freq= FALSE
) 

```

### Plotting Graphs - ggplot

```{r}

# ggplot2 

library(ggplot2)

#ggplot(my_data, aes(Age, Losses))

# ggplot(my_data, aes(Age, Losses)) + geom_bar(stat="identity") + 
#    guides(fill=TRUE) + ggtitle("Bar Chart of Age vs Losses")


p <- ggplot(my_data, aes(Age, Losses)) + 
        geom_line() +
        #geom_point() + 
        #guides(fill=TRUE) + 
        ggtitle("Bar Chart of Age vs Losses")

# displays as you require
require(scales)
p + scale_x_continuous(labels = comma)

#p + scale_x_discrete(labels = comma)

```

### Plotting Graphs - Plotly
```{r}

Married_status <- sqldf("select Married, count(Married) no_of_records from my_data group by Married")

p <- ggplot(Married_status, aes(x=Married,y=no_of_records , fill=Married)) +
    geom_bar(stat="identity")

ggplotly(p)

```


### Corelation

```{r Corelation}

#my_data <- read.csv("Lin_Reg_R.csv")

#View(my_data)

cor(my_data$Losses, my_data$Age)

# For cor to work all variables need to be in numeric 

cor(my_data[sapply(my_data,is.numeric)])

corr <- cor(my_data[sapply(my_data,is.numeric)])

# install.packages("corrplot")

corrplot::corrplot(corr)

```

### Regression analysis

```{r regression}

# Lets start with Independent variables 

#fit <- lm(dependent_variable ~ independent variable1 + independent variable2 , data = my_dataframe)

fit <- lm(capped_losses ~ Age + Years.of.Driving.Experience + Number.of.Vehicles + Vehicle.Age + Gender_Dummy + Marriage_Dummy  + Fuel_Dummy, data = my_data  )

# lm fits regression equation 

summary(fit)

# Find out multicollinearity ( value above 3 is high multicollinearity )


library(car)

vif(fit)

# Why Multicollinearity is a problem?
# Multicollinearity is a problem because it undermines the statistical significance of an independent variable. Other things being equal, the larger the standard error of a regression coefficient, the less likely it is that this coefficient will be statistically significant.

fit <- lm(capped_losses ~ Age +  Number.of.Vehicles + Vehicle.Age + Gender_Dummy + Marriage_Dummy + Fuel_Dummy, data = my_data  )

vif(fit)

summary(fit)

#Lets drop Number of vehicles varibale as t-value less

fit <- lm(capped_losses ~ Age +  Vehicle.Age + Gender_Dummy + Marriage_Dummy +  Fuel_Dummy, data = my_data  )

vif(fit)

summary(fit)

# Multiple R-squared:  0.7041,	Adjusted R-squared:  0.704 ~ 70%
# In general, the higher the R-squared, the better the model fits your data

my_pred <- predict(fit, type = "response")

head(my_pred)

my_residuals <- residuals(fit, type = "deviance")

head(my_residuals)

# plot predicted vs actuals losses 

plot(my_data$capped_losses, my_pred)


newdata <- data.frame(my_data$Policy.Number, my_data$capped_losses , my_pred , my_residuals)

View(newdata)

write.csv(newdata,file = "my_prediction_results.csv")

```

### Time Series 

```{r Time series}


library("tidyquant")

options("getSymbols.warning4.0"=FALSE)

options("getSymbols.yahoo.warning"=FALSE)
# Downloading Apple price using quantmod

getSymbols("AAPL", from = '2017-01-01',
           to = "2020-03-01",warnings = FALSE,
           auto.assign = TRUE)

head(AAPL)

class(AAPL)

chart_Series(AAPL)

chart_Series(AAPL['2017-12/2018-03'])


#We can download prices for several stocks. There are several steps to this

tickers = c("AAPL", "NFLX", "AMZN", "TSLA", "FB")

getSymbols(tickers,
           from = "2017-01-01",
           to = "2020-01-15")

library("purrr")

prices <- map(tickers,function(x) Ad(get(x)))

prices <- reduce(prices,merge)

colnames(prices) <- tickers

prices <- tq_get(tickers,
                 from = "2020-01-01",
                 to = "2020-07-21",
                 get = "stock.prices")


prices %>%
  group_by(symbol) %>%
  slice(1)

prices %>%
  ggplot(aes(x = date, y = adjusted, color = symbol)) +
  geom_line()


ggplotly(prices %>%
  ggplot(aes(x = date, y = adjusted, color = symbol)) +
  geom_line())


# Create a multiple line chart of the closing prices of the four stocks,
# showing each stock in a different color on the same graph.
# Transform the data so each stock begins at 100 and replot.
tq_get(c("GOOGL","AMZN","FB","AAPL"), get="stock.prices") %>%
  group_by(symbol) %>%
  mutate(close = 100*close/first(close)) %>%
  ggplot(aes(date, close, color=symbol)) +
  geom_line()


```

